\section{Conclusions}
\label{conclusions}

In this section, the objectives previously set will be analyzed. Furthermore, possible future work will be defined.

\subsection{Achieved objectives}

\begin{itemize}
  \item \textbf{Main goal: to develop a system to automatically assess a person’s drunkness based on the analysis of their eye(s) movement.} A complete system, composed by a mobile phone (camera and internet connection included) and a backend hosted in a server, has been developed and the functionality and usability of it has been tested by a small sample of people.
  \item \textbf{Secondary goals:}
  \begin{itemize}
    \item \textbf{To design a system that detects and tracks the user’s eyes and analyzes them in search of horizontal nystagmus movements.} The designed architecture is composed by the mobile application that, according to the proposed requirements, will record some videos to detect and track the eyes, send them to a server and proccess them.
    \item \textbf{To develop a system that detects and tracks the user’s eyes and analyzes them in search of horizontal nystagmus movements.} This goal has been achieved by means of analyzing the videos sent by the user and tracking the position of the eyes for every frame to check the movement looking for horizontal nystagmus movements.
    \item \textbf{To evaluate and test the previously mentioned system.} A small sample of people used the designed and developed application before and after drinking. These people have also taken an usability test to check the ease of use of the application.
  \end{itemize}
\end{itemize}

\subsection{Future work}

The mobile application 'Are-U-Drunk' could be improved in many ways. Some of the proposals for future work are:

\begin{itemize}
  \item Improve the algorith to be resilient to different illumination levels. This will result in a more accurate test result since the eyes and the gaze could be detected in more complicated scenarios.
  \item Create and train a new model from scrath. This could help the algorithm detect the eyes faster and better.
  \item Improve the user experience by features like clinging or vibrating when the camera stops recording.
  \item Link a video with a deeper explanation about the test and the clues so the user knows exactly how the video must be recorded.
\end{itemize}
